Who does big team science?

### 2023-04-20 manuscript_scopus.tex
finalizing pre-reg

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

\hypertarget{significance}{%
\section{Significance}\label{significance}}

@@

The credibility movement has been mirrored by the calls for
diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018) and
Biology (Collins et al., 2003), the social sciences struggle to represent the
breadth of humanity across both researcher and population
characteristics. Now, grassroots organizations, such as the
Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
(\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}), and
DRAGNet (\url{https://dragnetglobal.weebly.com/}) can begin to tackle these
issues by recruiting research labs from all over the globe to provide
diversity in geographic, linguistic, and researcher representation.
Publications have examined the global understanding of morality, face
processing, COVID-19 information signaling, and more (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Van Bavel et al., 2022; Wang et al., 2021). While
these organizations and one-time groups for BTS studies have provided an
incredible wealth of data for the scientific community, we do not yet
know exactly \emph{who} is involved with, and benefits from, the BTS and
credibility movement. Publications on BTS generally explore challenges,
lessons learned, the need for BTS (Coles et al., 2022; Forscher et al., 2020).

@@

\hypertarget{approach}{%
\section{Approach}\label{approach}}

@@

We have defined \textbf{BTS publications} as publications with at least 10
authors at 10 different institutions that were published in
peer-reviewed journals or had posted a full paper pre-print. We will use
data from 1970 and forward in the publications (\texttt{ani)} database, as it
is noted online that this time period includes cited references for
calculation of several of our variables described below. We will analyze
our results based on the big four subject areas: Physical Sciences,
Health Sciences, Social Sciences, and Life Sciences.

@@

Using these criteria, we will extract the following information for
publication sources: the name of the publication (source title), subject
area (both the large four subject areas and the smaller four digit all
science journal classification ASJC codes). We will examine journal
impact using the Source Normalized Impact per Paper from the journal
(\texttt{sources)} database.

@@

\textbf{\emph{Institution}}. We will use the affiliation ids and country to gather
information about the places of education and/or employment for authors.
Country will likely be binned into United Nation Sub-Region for
analyses.

@@

\textbf{\emph{Publication Metrics}}. For each author, we will calculate the total
number of publications, the h-index, and the i-10 index. The h-index
represents the highest \emph{h} number of publications that have at least \emph{h}
citations, while the i-10 index represents the number of publications
with at least 10 citations.

@@

\begin{itemize}
\tightlist
\item
  Number of articles for inclusion: total, separated by four subject
  areas, presenting graphics of the number of publication across time
\item
  Number of distinct journals within each of the four subject areas
\item
  Statistics (mean, median, standard deviation, minimum, maximum) of
  the journal impact using Source Normalized Impact per Paper for the
  four subject areas.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The totals of the number of articles published within the smaller
  subject area classifications. We will visualize these differences
  over time to determine if there is increasing interest in a specific
  subarea over time for each of the four larger subject area
  classifications.
\item
  The keywords present in the publications data overall to identify
  trends and common themes in the publications for the four subject
  areas using visualizations (wordclouds) to depict the common
  keywords.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  The total number of unique authors
\item
  Statistics (mean, standard deviation, minimum, maximum, median) on
  the number of authors included on publications.
\item
  We will present visualizations of these results across time.
\end{itemize}

We will use \(\alpha\) \textless{} .05 for all analyses that involve hypothesis
testing. We make no directional predictions.

@@

\begin{itemize}
\tightlist
\item
  We will create a visualization of the trend and variance of
  researcher career length across publication years.
\item
  To analyze trends over time, we will calculate the average career
  length for each publication (i.e., average the author career length
  to create one score for each paper) and run a regression analysis
  using career length to predict year of publication. A positive slope
  for year of publication would indicate increasing years of first
  publication (i.e., more younger scholars over time), while a
  negative slope would indicate older years of first publication
  (i.e., more older scholars over time).
\item
  In order to show variance between individuals, we calculate the
  standard deviation of career length for each publication and run a
  regression analysis using this variance representation to predict
  publication year. A positive slope would indicate increasing
  variance over time (i.e., more diversity in the career lengths of
  scholars), while a negative slope would indicate less variance and
  diversity in scholars over time.
\item
  These analyses will be completed separately for each of the four
  large subject areas.
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  We will summarize the general education categories of individuals at
  the time of publication, along with a summary for change over time.
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  We will report descriptive statistics on the total number of
  publications, i10 index, and h-index for individuals overall.
\item
  Next, we will use the same analyses described in the career length
  section to analyze trends over time. An increasing slope over time
  indicates that individuals who are publishing more are more
  represented in BTS over time (i.e., increasing numbers of scholars
  with higher publication rates), while a negative slope indicates
  more researchers with less publications.
\item
  A positive slope for standard deviation indicates increasing
  variance over time (i.e., more diversity in the individual
  publication rates), while a negative slope would indicate less
  diversity in researchers over time. While publication rates do not
  represent value as a researcher, they are often used in hiring and
  promotion decisions, and we will use this variable as a proxy to
  gauge the diversity in scholars represented in big teams.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  We will present visualizations of the country information listed for
  authors, and we will discuss the areas of world in which authors
  generally come from, as well as the lowest representation of
  authors.
\item
  To understand the change in representation diversity, we will
  summarize the total number of geopolitical regions for each paper.
  Using a linear model, we will examine if the number of regions
  present is predicted by the year of publication. Increasing
  diversity would be represented by a positive slope, while decreasing
  diversity would be represented by a negative slope.
\item
  Last, we will examine the differences in representation for
  corresponding author sets versus all other authors. For papers with
  10 to 49 authors, we will use the three first authors and the last
  author to compare against other authors. For 50 to 99 authors, five
  first authors plus last will be used, and for all papers with more
  than 100 authors, we will use ten first authors and the last author.
  We will calculate the frequencies of each of the UN Sub-Regions for
  first authors versus other authors, converting these values to
  proportions. Given the expected small sample sizes of these
  contingency tables, we will group together titles based on the year
  of publication (assuming at least 5 publications per year, these may
  be binned by 5-year or smaller increments to increase sample size).
  For each grouping, we will calculate the effect size of the
  differences in frequencies comparing first authors to all other
  authors. Since this data is categorical, we will use Cramer's V to
  represent the effect size. If the effect size includes zero in its
  confidence interval, this result will imply that first and all other
  authors represent the same pattern of UN Sub-Region diversity. Any
  confidence interval that does include zero represents a difference
  in diversity. We will report these values and discuss what regions
  of the world are represented when effect sizes indicate a different
  from zero using standardized residuals.
\end{itemize}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

@@

The credibility movement has been mirrored by the calls for
diversification or de-WEIRDing (e.g., Western, Educated, Industrialized,
Rich, and Democratic) scientific research (Henrich et al., 2010; Newson et al., 2021; Rad et al., 2018) by improving representation in research samples. Like the
large-scale studies in Physics ({``A Philosophical Case for Big Physics,''} 2021; Castelnovo et al., 2018) and
Biology (Collins et al., 2003), the social sciences struggle to represent the
breadth of humanity across both researcher and population
characteristics. Now, grassroots organizations, such as the
Psychological Science Accelerator (Moshontz et al., 2018), ManyBabies
(\url{https://manybabies.github.io/}), NutNet (\url{https://nutnet.org/}), and
DRAGNet (\url{https://dragnetglobal.weebly.com/}) can begin to tackle these
issues by recruiting research labs from all over the globe to provide
diversity in geographic, linguistic, and researcher representation.
Publications have examined the global understanding of morality, face
processing, COVID-19 information signaling, and more (Bago et al., 2022; Dorison et al., 2022; Jones et al., 2021; Legate et al., 2022; Van Bavel et al., 2022; Wang et al., 2021). While
these organizations and one-time groups for BTS studies have provided an
incredible wealth of data for the scientific community, we do not yet
know exactly \emph{who} is involved with, and benefits from, the BTS and
credibility movement. Publications on BTS generally explore challenges,
lessons learned, and the need for BTS (Coles et al., 2022; Forscher et al., 2020).

@@

\hypertarget{research-questions}{%
\section{Research Questions}\label{research-questions}}

@@

We have defined \textbf{BTS publications} as publications with at least 10
authors at 10 different institutions that were published in
peer-reviewed journals or had posted a full paper pre-print. We will use
data from 1970 and forward in the publications (\texttt{ani}) database, as it
is noted online that this time period includes cited references for
calculation of several of our variables described below. We will analyze
our results based on the big four subject areas: Physical Sciences,
Health Sciences, Social Sciences, and Life Sciences. We filtered the
database to include articles, articles in press, business articles,
conference papers, data papers, preprints, and surveys using Elsevier's
classification system.

@@

Using these criteria, we will extract the following information for
publication sources: the name of the publication (source title), subject
area (both the large four subject areas and the smaller four digit all
science journal classification ASJC codes). We will examine journal
impact using the Source Normalized Impact per Paper from the journal
(\texttt{sources}) database.

@@

\textbf{\emph{Institution and Geopolitical Region}} . We will use the affiliation
ids and country to gather information about the places of education
and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.

@@

\textbf{\emph{Publication Metrics}}. For each author, we will calculate the total
number of publications, and the h-index. The h-index represents the
highest \emph{h} number of publications that have at least \emph{h} citations.

@@

\begin{itemize}
\tightlist
\item
  Number of articles for inclusion: total, separated by four subject
  areas, presenting graphics of the number of publication across time
  total
\end{itemize}

\emph{Number of articles}. The total number of articles included in this analysis was 13581 including 10685 Health Sciences articles, 6151
Physical Sciences articles, 543 Social Sciences articles, and
7686 Life Sciences articles. Articles could be classified into
multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-time-1.pdf}
\caption{\label{fig:fig-pub-time}Number of big-team science publications separated by four large subject areas across years.}
\end{figure}

\begin{itemize}
\tightlist
\item
  Number of distinct journals within each of the four subject areas
\end{itemize}

\emph{Number of journals}. The number of distinct journals big team science articles were published
in was 2534 with 1472 journals in Health Sciences,
641 journals in Physical Sciences, 206
journals in Social Sciences, and 1024 journals in Life
Sciences. The descriptive statistics for the Source Normalized Impact
per Paper is presented in Table X. For comparison, the SNIP descriptive
statistics for all papers is shown in Table X.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tab-snip}Big-Team Science SNIP Values}

\begin{tabular}{llllll}
\toprule
Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
\midrule
Health Sciences & 4.40 & 7.18 & 0.00 & 2.08 & 173.93\\
Physical Sciences & 1.73 & 1.34 & 0.16 & 1.28 & 30.40\\
Social Sciences & 2.20 & 2.14 & 0.02 & 1.60 & 30.40\\
Life Sciences & 2.52 & 2.04 & 0.02 & 1.74 & 12.62\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:unnamed-chunk-3}All Journal Articles SNIP Values}

\begin{tabular}{llllll}
\toprule
Subject Area & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Minimum} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{Maximum}\\
\midrule
Health Sciences & 2.13 & 4.21 & 0.00 & 1.44 & 173.93\\
Physical Sciences & 1.48 & 1.10 & 0.00 & 1.26 & 30.40\\
Social Sciences & 1.98 & 1.41 & 0.00 & 1.66 & 30.40\\
Life Sciences & 1.53 & 1.23 & 0.00 & 1.24 & 19.07\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

@@

\begin{itemize}
\tightlist
\item
  The totals of the number of articles published within the smaller
  subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-clouds-1.pdf}
\caption{\label{fig:fig-clouds}Journal Areas for Big-Team Science Publications by Subject Area}
\end{figure}

\begin{itemize}
\tightlist
\item
  The keywords present in the publications data overall to identify
  trends and common themes in the publications for the four subject
  areas using visualizations (wordclouds) to depict the common
  keywords.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-keywords-1.pdf}
\caption{\label{fig:fig-keywords}Keyword Analysis for Each of the Four Subject Areas.}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  The total number of unique authors
\end{itemize}

The total number of unique authors across all publications was
257536.

\begin{itemize}
\tightlist
\item
  Statistics (mean, standard deviation, minimum, maximum, median) on
  the number of authors included on publications.
\end{itemize}

The mean number of authors per publication was \emph{M} = 49.90
(\emph{SD} = 207.01, \emph{Med} = 19) with a range of
10 to 5155.

\begin{itemize}
\tightlist
\item
  We will present visualizations of these results across time.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-author-year-1.pdf}
\caption{\label{fig:fig-author-year}Number of authors included on big-team science papers per year by subject area. Colored dots indicate the mean number of authors, while the black dots represent the median number of authors. The size of the black dots indicate the number of papers in that year.}
\end{figure}

We will use the 95\% confidence interval to make all claims of predictors
or effects different zero. The confidence interval that does not include
zero would be considered different from zero (to four decimal places).
We make no directional predictions.

@@

\begin{itemize}
\tightlist
\item
  We will create a visualization of the trend and variance of
  researcher career length across publication years.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-career-1.pdf}
\caption{\label{fig:fig-career}Average career length for big-team science authors. Larger dots indicate more papers for each estimation. Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length.}
\end{figure}

\begin{itemize}
\tightlist
\item
  To analyze trends over time, we will calculate the average career
  length for each publication (i.e., average the author career length
  to create one score for each paper) and run a regression analysis
  using career length to predict year of publication. In order to show
  variance between individuals, we calculate the standard deviation of
  career length for each publication and run a regression analysis
  using this variance representation to predict publication year.
  These two variables will be used together.
\item
  Negative slopes would indicate more young scholars in later years
  (i.e., lower average career length as time increases). Positive
  slopes would indicate older scholars in later years (i.e., higher
  average career length as time increases).
\item
  Negative slopes imply that variability decreases over the years, so
  the average career length is more homogeneous. Positive slopes imply
  that variability increases over the years, so the average career
  length is varied across individuals (lots of different types of
  scholars).
\item
  These analyses will be completed separately for each of the four
  large subject areas.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-career-results-1.pdf}
\caption{\label{fig:fig-career-results}Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication.}
\end{figure}

@@

The total number of unique affiliation across all papers was 35114.

\begin{verbatim}
## Warning: Groups with fewer than two data points have been dropped.
## Groups with fewer than two data points have been dropped.
## Groups with fewer than two data points have been dropped.
\end{verbatim}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-inst-1.pdf}
\caption{\label{fig:fig-inst}Number of unique institutions involved in big-team science papers across decades.}
\end{figure}

@@

We will summarize the general education categories of individuals at the
time of publication, along with a summary for change over time.

\begin{itemize}
\tightlist
\item
  For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are ``normal'' academics/researchers)
\item
  We will only perform this analysis if the proportion of information avaliable is over 50\%.
\end{itemize}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1250}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1250}}@{}}
\toprule()
\endhead
d
egrees & count \\
\begin{minipage}[t]{\linewidth}\raggedright
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{F7FA46}

\NormalTok{  null}

\NormalTok{    MD}

\NormalTok{   PhD}
\NormalTok{M}
\NormalTok{D, PhD}

\NormalTok{  M.D.}

\NormalTok{   Dr.}

\NormalTok{   MSc}

\NormalTok{   MPH}
\end{Highlighting}
\end{Shaded}

Prof.,
PhD
Ph.D.
MS MD
PhD
MD.
Prof.
MD
Prof.
PhD BS
Prof
BA
M.D.,
Ph.D.
MD,
MPH
\end{minipage} & 656440
8190
3879
1267
1002
490
461
368
349
348
330
285
279
266
239
232
220
196
191
158 \\
\bottomrule()
\end{longtable}

@@

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-types-1.pdf}
\caption{\label{fig:fig-pub-types}Types of publications for big-team science and all authors.}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  We will report descriptive statistics on the total number of
  publications and h-index for individuals overall.

  \begin{itemize}
  \tightlist
  \item
    Do this for each unique person and report averages
  \item
    Do this for each publication and create an average for each
    publication
  \end{itemize}
\end{itemize}

The average number of publications by authors on big team sciences
papers is \emph{M} = 4.45 (\emph{SD} =
6.90). The publication counts were averaged across
authors for each publication, and then these average publication counts
were averaged across publications \emph{M} = 7.58 (\emph{SD} =
5.80). The average variability (i.e., the average
standard deviation with authors of a manuscript) with publication counts
of a paper was \(M_{SD}\) = 7.14 (\(SD_{SD}\) =
5.10).

The same process was completed with \emph{h}-index for each author and
publication. The average \emph{h}-index for authors overall was \emph{M} =
14.24 (\emph{SD} = 43.80, \emph{Med} = 2.00). The
average \emph{h}-index for publications was \emph{M} = 28.14 (\emph{SD}
= 38.01), and the variability of \emph{h}-index across
manuscripts was \(M_{SD}\) = 36.43 (\(SD_{SD}\) =
46.47, \(Med_{Med}\) = 5.00).

\begin{itemize}
\tightlist
\item
  Next, we will use the same analyses described in the career length
  section to analyze trends over time. An increasing slope over time
  indicates that individuals who are publishing more are more
  represented in BTS over time (i.e., increasing numbers of scholars
  with higher publication rates), while a negative slope indicates
  more researchers with less publications.
\item
  A positive slope for standard deviation indicates increasing
  variance over time (i.e., more diversity in the individual
  publication rates), while a negative slope would indicate less
  diversity in researchers over time. While publication rates do not
  represent value as a researcher, they are often used in hiring and
  promotion decisions, and we will use this variable as a proxy to
  gauge the diversity in scholars represented in big teams.
\item
  We will separate these by each of the four subject areas.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-pub-results-1.pdf}
\caption{\label{fig:fig-pub-results}Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication.}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  We will present visualizations of the country information listed for
  authors, and we will discuss the areas of world in which authors
  generally come from, as well as the lowest representation of
  authors.
\end{itemize}

\begin{verbatim}
## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN

## Warning in countrycode_convert(sourcevar = sourcevar, origin = origin, destination = dest, : Some values were not matched unambiguously: ANT, EUE, TWN
\end{verbatim}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-map-both-1.pdf}
\caption{\label{fig:fig-map-both}Geopolitical regions represented in big-team science publications versus all publications.}
\end{figure}

\begin{itemize}
\tightlist
\item
  To understand the change in representation diversity, we will
  summarize the total number of geopolitical regions for each paper.
  Using a linear model, we will examine if the number of regions
  present is predicted by the year of publication. Increasing
  diversity would be represented by a positive slope, while decreasing
  diversity would be represented by a negative slope.
\end{itemize}

\begin{figure}
\centering
\includegraphics{manuscript_scopus_files/figure-latex/fig-diversity-1.pdf}
\caption{\label{fig:fig-diversity}Number of geopolitical regions and variance in the number of regions represented in big-team science publiactions predicting time and the overall mode effect size.}
\end{figure}
